---
title: "Career talk"
subtitle: "Alfred University biology seminar"
author: "Leslie Emery"
date: "November 12, 2021"
output:
  xaringan::moon_reader:
    css: [xaringan-themer.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = FALSE, message = FALSE, dpi = 72)
```

```{r xaringan-themer, include = FALSE}
library(xaringanthemer)
mono_light(
  base_color = "#125972", ## picked to coordinate with rOpenSci logo
  code_highlight_color = "#c0e8f5",
  link_color = "#197b9e",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Droid Mono")
)
```


# Overview

* Hometown: Lansing, MI; Current city: Seattle, WA
* Alfred Biology major, 2004 - 2008
* University of Washington Genome Sciences PhD 2008 - 2014
* Research Scientist, UW Biostatistics Genetic Analysis Center 2014 - 2019
* Insight Data Science 2020
* Principal Data Scientist, Bristol Myers Squibb, 2020 - present

---

# My time at Alfred

* National Merit Scholarship
* Major indecision
    * English, Fine art, and finally Biology in 1st year
* Honors Program

---

# My Alfred highlights

* 2 independent study research projects (ARGUS grants)
    * Animal behavior - how mice and gerbils react to strangers
    * Evolutionary biology - comparing gene sequences of lemurs
* ITS Helpdesk sophomore - senior years
    * Technician, Student Manager, and then Student Director

---

# REU internship at University of Michigan

* Evolutionary biology lab studying insects
* Extracting DNA from grasshoppers ("wet lab")
* Analyzing data from *Drosophila* DNA sequences to infer evolutionary history of two species

---

# Applying to grad school

* 6 interviews in ~2 months (too many!)
    * Accepted: Penn State, Rutgers, Ohio State, U Washington (UW)
    * Not accepted: U Mich, Cornell
* UW Genome Sciences
    * Seattle is amazing
    * Professors were friendly, interesting
    * Grad students were happy, friendly, welcoming

---

# Grad school and beyond

* UW Genome Sciences
    * Year 1: lab rotations & projects, classes
    * Year 2: classes, general exam (research proposal)
    * Years 3 - 5.5: research
    * Studied human evolutionary history from existing patterns of genetic variation
* Research scientist, UW Biostatistics (5 years)

---

# Bristol Myers Squibb

.left-column[
## Tasks
* Data processing
* Data analysis
* Plots & charts
* Interactive visualizations
]

.right-column[
## Questions
* What are promising treatments for diseases with unmet needs?
* How does a particular treatment work?
* Do existing treatments work particularly well/particularly poorly for specific subsets of patients?
* What are the long term effects of existing treatments?
* Cancer, cardiovascular disease, immune diseases, etc.
]

---

# If I had it to do over...

* Industry internship (undergrad and graduate)
* Talking to those in careers of interest
* More statistics classes
* Intro coding classes
* Study abroad

---

# Alfred's unique advantages

* Getting to know your professors
    * Personalized recommendation letters
* Class presentations
* Alumni network

---

# Contact me

*Especially if you're interested in coding, data analysis, statistics, or pharma!*

* [Linkedin]()
* Email: leslie.s.emery@gmail.com

